---
title: "BKM_Assignment"
author: "Bulent Buyuk"
date: "10 11 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1.Introduction & Import Packages

This is a worksheet of BKM Sektorel Gelisim Assignment.

The assignment's dataset includes the January 2019 through June 2019.

We import packages we'll use.

````{r warning=FALSE,message=FALSE}

library("rvest")
library("tidyverse")
library("lubridate")

````

# 2.Get BKM Dataset

We downloaded dataset from the [BKM website](https://bkm.com.tr/secilen-aya-ait-sektorel-gelisim/) separately for each month. 

Then, we create tables for each month.

````{r warning=FALSE,message=FALSE}

raw6<- read_html("https://bkm.com.tr/secilen-aya-ait-sektorel-gelisim/?filter_year=2019&filter_month=6&List=Listele")
raw5<- read_html("https://bkm.com.tr/secilen-aya-ait-sektorel-gelisim/?filter_year=2019&filter_month=5&List=Listele")
raw4<- read_html("https://bkm.com.tr/secilen-aya-ait-sektorel-gelisim/?filter_year=2019&filter_month=4&List=Listele")
raw3<- read_html("https://bkm.com.tr/secilen-aya-ait-sektorel-gelisim/?filter_year=2019&filter_month=3&List=Listele")
raw2<- read_html("https://bkm.com.tr/secilen-aya-ait-sektorel-gelisim/?filter_year=2019&filter_month=2&List=Listele")
raw1<- read_html("https://bkm.com.tr/secilen-aya-ait-sektorel-gelisim/?filter_year=2019&filter_month=1&List=Listele")

raw_table6 <- raw6%>% html_table(fill = TRUE)
raw_table5 <- raw5%>% html_table(fill = TRUE)
raw_table4 <- raw4%>% html_table(fill = TRUE)
raw_table3 <- raw3%>% html_table(fill = TRUE)
raw_table2 <- raw2%>% html_table(fill = TRUE)
raw_table1 <- raw1%>% html_table(fill = TRUE)

table6<-raw_table6[[4]]
table5<-raw_table5[[4]]
table4<-raw_table4[[4]]
table3<-raw_table3[[4]]
table2<-raw_table2[[4]]
table1<-raw_table1[[4]]

````

# 3. Data Transformation

We add a date column to each table and change the names of all columns.

Then, we merge the tables by filtering the rows.

```{r warning=FALSE,message=FALSE}

table6<-add_column(table6,yeni="2019-06-30")
table5<-add_column(table5,yeni="2019-05-31")
table4<-add_column(table4,yeni="2019-04-30")
table3<-add_column(table3,yeni="2019-03-31")
table2<-add_column(table2,yeni="2019-02-28")
table1<-add_column(table1,yeni="2019-01-31")

names(table1)<- c("Isyeri_Grubu","Islem_Adedi_Kredi_Karti","Islem_Adedi_Banka_Karti","Islem_Tutari_Kredi_Karti","Islem_Tutari_Banka_Karti","Tarih")
names(table2)<- c("Isyeri_Grubu","Islem_Adedi_Kredi_Karti","Islem_Adedi_Banka_Karti","Islem_Tutari_Kredi_Karti","Islem_Tutari_Banka_Karti","Tarih")
names(table3)<- c("Isyeri_Grubu","Islem_Adedi_Kredi_Karti","Islem_Adedi_Banka_Karti","Islem_Tutari_Kredi_Karti","Islem_Tutari_Banka_Karti","Tarih")
names(table4)<- c("Isyeri_Grubu","Islem_Adedi_Kredi_Karti","Islem_Adedi_Banka_Karti","Islem_Tutari_Kredi_Karti","Islem_Tutari_Banka_Karti","Tarih")
names(table5)<- c("Isyeri_Grubu","Islem_Adedi_Kredi_Karti","Islem_Adedi_Banka_Karti","Islem_Tutari_Kredi_Karti","Islem_Tutari_Banka_Karti","Tarih")
names(table6)<- c("Isyeri_Grubu","Islem_Adedi_Kredi_Karti","Islem_Adedi_Banka_Karti","Islem_Tutari_Kredi_Karti","Islem_Tutari_Banka_Karti","Tarih")

table6<-slice(table6,3:28)
table5<-slice(table5,3:28)
table4<-slice(table4,3:28)
table3<-slice(table3,3:28)
table2<-slice(table2,3:28)
table1<-slice(table1,3:28)

bkm_data<-bind_rows(table1, table2, table3, table4, table5, table6)

glimpse(bkm_data)

```

We convert numeric and date columns because all columns of our dataset are characters.

We are ready for analysis!

```{r warning=FALSE,message=FALSE}

bkm_data$Tarih <- ymd(bkm_data$Tarih)

bkm_data$Islem_Adedi_Kredi_Karti<-as.numeric(gsub("\\.","",bkm_data$Islem_Adedi_Kredi_Karti))
bkm_data$Islem_Adedi_Banka_Karti<-as.numeric(gsub("\\.","",bkm_data$Islem_Adedi_Banka_Karti))
bkm_data$Islem_Tutari_Kredi_Karti<-as.numeric(gsub(",",".",gsub("\\.","",bkm_data$Islem_Tutari_Kredi_Karti)))
bkm_data$Islem_Tutari_Banka_Karti<-as.numeric(gsub(",",".",gsub("\\.","",bkm_data$Islem_Tutari_Banka_Karti)))

glimpse(bkm_data)

```

# 4. Analysis

## Sectoral Transaction Volume

```{r warning=FALSE,message=FALSE}

sektor_orani<- bkm_data %>%
  select(Isyeri_Grubu,Islem_Adedi_Kredi_Karti,Islem_Adedi_Banka_Karti,Islem_Tutari_Kredi_Karti,Islem_Tutari_Banka_Karti,Tarih) %>%
  group_by(Isyeri_Grubu) %>%
  summarize(islem_hacmi=sum(Islem_Tutari_Kredi_Karti,Islem_Tutari_Banka_Karti)) %>%
  mutate(oran = round(islem_hacmi/sum(islem_hacmi),2)) %>%
  arrange(desc(oran)) %>%  
  print(sektor_orani)

en_iyi_on_sektor<-head(sektor_orani,10)
ggplot(data = en_iyi_on_sektor, aes(x=Isyeri_Grubu, y=oran, fill=Isyeri_Grubu)) +
  geom_bar(stat="identity")+
  coord_polar()+
  theme(legend.position = "right", axis.text.x = element_text(angle = 0))+
  geom_text(aes(y = oran , label = oran))+
  labs(title = "Sector Shares", x="", y="")

```

## Monthly Transaction Volume

```{r warning=FALSE,message=FALSE}

aylik<- bkm_data %>%
  arrange(desc(Tarih),desc(Islem_Tutari_Kredi_Karti)) %>%
  group_by(Tarih) %>%
  summarize(aylik_kartlar_toplami = sum(Islem_Tutari_Kredi_Karti, Islem_Tutari_Kredi_Karti)) %>%
  arrange(desc(aylik_kartlar_toplami))%>%
  print(aylik)
  
ggplot(data = aylik, aes(x = workplace, y = aylik_kartlar_toplami, fill = as.character(Tarih)))+ 
  geom_bar(stat = "identity") + 
  aes(x = reorder(Tarih, -aylik_kartlar_toplami),y =aylik_kartlar_toplami) + 
  labs(x = "", y = "", title = "Monthly Transaction Volume") + 
  theme_bw() + theme( axis.text.x = element_text(angle = 90,vjust = 0.49, hjust = 0.49, size = 8)) + 
  scale_y_continuous(labels = scales::comma) + 
  scale_x_discrete(labels = c("Mayis", "Haziran","mart", "Nisan", "ocak", "Subat")) + 
  theme(legend.position = "none")

```
